Mapping Properties of Surface Source Extension

### 2025-03-22 repro/papers/ssefound/paper.tex
more

\section{Symmetric Hyperbolic Systems}
$k \times  k$ symmetric hyperbolic system: in $\bR^{n+1}$. Suppose that $u \in L^2_{\rm loc}(\bR^{n+1},\bR^k)$ is a weak solution of
\begin{equation}
  \label{eqn:shs}
  (\sum_{i=0}^n A_i\partial_i ) u \in L^2_{\rm loc}(\bR^{n+1},\bR^k)
\end{equation}
The coefficieent matrices $A_i \in C^{\infty}(\bR^n, \bR^{k \times k}), i=0,...,n$ are symmetric.

@@

Notation:$x_0=t$, $\partial_t=\partial_0$, $\bx = (x_1,...,x_n)$, $D=(\partial_1,...\partial_n)$
\[
  K(t,\bx,D)= \sum_{i=1}^n A_i(t,\bx)\partial_i, \, M(t,\bx) = A_0(t,\bx).
\]
If $M$ is positive definite, trace properties coverd by standard theory (above). Let $\Pi_0(t,\bx)$ = projection on null space $V_0$ of $M(t,\bx)$, $\Pi_1=I-\Pi_0$ = projection on range $V_1$. Denote the rank of $M$ by $l={\rm dim} V_1$ Then
\[
  M\partial_t u + Ku = \Pi_1 M \partial_t \Pi_1 u + \sum_{\alpha,\beta=0,1} \Pi_{\alpha}K\pi_{\beta}u + \mbox{ l.o.t. }
\]
Since the ranges are orthogonal,
\begin{eqnarray}
  \Pi_1 M \partial_t \Pi_1 u + \Pi_1 K \Pi_1 u + \Pi_1 K \Pi_0 u & \in & L^2_{\rm loc}(\bR^{n+1},V_1),
  \label{eqn:decomp1} \\
  \Pi_0 K \Pi_0 u + \Pi_0 K \Pi_1 u & \in & L^2_{\rm loc}(\bR^{n+1},V_0)
  \label{eqn:decomp0}
\end{eqnarray}
Set $K_{\alpha,\beta} = \Pi_{\alpha}K\Pi_{\beta}$.

@@

% Suppose that $\Gamma_0, \Gamma \subset T^*(\bR^n)$ are conic open sets with $\overbar{\Gamma_0 \subset \Gamma$ and $\delta t >0$. Assume that  that for $|t|\le \delta t$ and $(\bx,\xi) \in Gamma$, $K_{00}(0,\bx,\xi)$ is invertible as a map $V_0 \rightarrow V_0$.
Let  $L_{00}(t,\bx,\xi) \in C^{\infty}(\bR, S^{-1}(\bR^n))$ be inverse to $K_{0,0}(t,\bx,\xi)$ on $V_0$: that is,
\[
  K_{0,0}(t,\bx,\xi)L_{0,0}(t,\bx,\xi) v=v=L_{0,0}(t,\bx,\xi)K_{0,0}(t,\bx,\xi)v
\]
for all $v \in V_0$. Construct $L_{0,0}$ to be homogeneous of degree -1 outside of a neighborhood of $\xi=0$, with $V_1$ an invariant subspace for $L_{0,0}(t,\bx,\xi)$ on which it vanishes. It follows that $L_{0,0}$ is symmetric, and that
\[
  \Pi_0 u - L_{0,0}K_{0,0}\Pi_u = \Pi_0 u - L_{0,0}K_{0,0}u = \Pi_0 u + L_{0,0}K_{0,1}u \in H^{-1}_{\rm loc}(\bR^{n+1})^k
\]
so
\[
  K_{1,0}u + K_{1,0}L_{0,0}K_{0,1}u \in L^2 _{\rm loc}(\bR^{n+1})^k
\]
Define
\[
  \tilde{K} = K_{11} - K_{10}L_{00}K_{01}.
\]
Then \ref{eqn:decomp1} can be rewritten
\begin{equation}
  \label{eqn:shs1}
  M\partial_t u_1 + \tilde{K}u_1 \in L^2_{\rm loc}(\bR^{n+1},V_1)
\end{equation}
Note that for each $t \in \bR, (\bx,\xi) \in T^*(\bR^n)$, both $V_0$ and $V_1$ are invariant subspaces of $\tilde{K}(t,\bx,\xi)$, and $V_0 \subset {\rm ker}(\tilde{K}(t,\bx,\xi)$. Also, $M$ is invertible when restricted to $V_1 = {\rm Rng} M = {\rm Rng } \Pi_1$ , but not (necessarily) positive definite.

Diagonalization: for $(t,\bx,\tau,\xi) \in T^*(\bR^n)$, define the restricted characteristic polynomial
\[
  {\cal C}(t,\bx,\tau,\xi) = \det (M(t,\bx)\tau + \tilde{K}(t,\bx,\xi) )= 0
\]
Since $V_0$ and $V_1$ are invariant subspaces of the matrix in parentheses, and $V_0$ is (contained in) its null space, there are at most $l={\rm dim}V_1$ non-zero roots in $\tau$ for $\xi \ne 0$.

@@

For each $\tau_i, i =1,...m$, choose $U_i(t,\bx,\xi) \in C^{\infty}(\bR \times T^*(\bR^n),V_1(t,\bx))$,  so that
\[
  \tau_i M(\bx) U_i(t,\bx,\xi) + \tilde{K}(t,\bx,\xi) U_i(t,\bx,\xi)=0, \, i=1,..,m.
\]
$U_1,...,U_m$ span a subspace $\tilde{V}_1(t,\bx,\xi)$. Scale $U_i$ so that $|U_i(t,\bx,\xi)| = |\xi|$.

Note that $\tau_i(t,\bx,\xi), i=1,...,m$ are homogeneous of order 1 in $\xi$ and smooth in $\bx$, $U_i(t,\bx,\xi), i=1,...,m$ are homogeneous of order 0 in $\xi$, smooth in $\bx$. So both are symbol-valued functions, of orders 1 and 0 respectively. Since the $U$'s must be orthogonal, $U_i^TU_j = |\xi|^2\delta_{ij}$.

@@

Set $u=(p,v_x,v_z), \bx=(t,x), \xi=(\omega,\xi_x), z \mapsto t$. Then \ref{eqn:awe} takes the form \ref{eqn:shs} with
\[
  M =
  \left(
    \begin{array}{ccc}
      0 & 0 & 1\\
      0 & 0 & 0\\
      1 & 0 & 0
    \end{array}
  \right),
  A_1 ={\rm diag}\left(\frac{1}{\kappa},\rho,\rho\right),
  A_2 =
 \left(
    \begin{array}{ccc}
      0 & 1 & 0\\
      1 & 0 & 0\\
      0 & 0 & 0
    \end{array}
  \right),
\]
So $V_0={\rm span}(\{e2\}),\, V_1={\rm span}(\{e1,e3\}), \Pi_0 = {\rm diag}(0,1,0)$ 
\[
  K(t,\bx,\xi) =  A_1(\bx) \xi_1 + A_2(\bx) \xi_2 =
  \left(
    \begin{array}{ccc}
      \frac{1}{\kappa(\bx)}\omega & \xi_x & 0 \\
      \xi_x & \rho(\bx) \omega & 0 \\
      0 & 0 & \rho(\bx) \omega
    \end{array}
  \right)
\]
whence $K_{0,0} = {\rm diag}(0, \rho(\bx) \omega, 0)$.
\[
  K_{1,1}(t,\bx,\xi) =
  \left(
    \begin{array}{ccc}
      \frac{1}{\kappa(\bx)}\omega & 0 & 0 \\
      0 & 0 & 0 \\
      0 & 0 & \rho(\bx) \omega
    \end{array}
  \right),
\]
\[
  K_{0,1}(t,\bx,\xi) =
  \left(
    \begin{array}{ccc}
      0 & \xi_x & 0 \\
      0 & 0 & 0 \\
      0 & 0 & 0
    \end{array}
  \right)
\]
and $K_{1,0} = K_{0,1}^T$.

@@

\begin{proof}
  For $u \in \Ciz(\bR^n)$,
  \[
    {\cal F}_x(Hu)(\xi',y) = \int  d\eta H(\xi',\eta')\hat{u}(\xi',\eta)e^{ i y \eta}
  \]
  So
  \[
    (P\phi H)u(x,y) = \int d \xi P(x,y,\xi) {\cal F}_x(\phi Hu)(\xi,y)e^{i x\xi}
  \]
  \[
    =\int d \xi' \int d \xi P(x,y,\xi) {\cal F}_x\phi(\xi-\xi',y) {\cal F}_x(Hu)(\xi',y)e^{i x\xi}
  \]
  \[
   =\int d \xi' \int d \xi \int d\eta P(x,y,\xi) {\cal F}_x\phi(\xi-\xi',y) H(\xi',\eta)\hat{u}(\xi',\eta)e^{i x\xi + i y\eta }
  \]
  \[
    =\int d \xi' \int d \xi \int d\eta P(x,y,\xi) {\cal F}_x\phi(\xi-\xi',y) e^{ix(\xi-\xi')}H(\xi',\eta)\hat{u}(\xi',\eta)e^{i x\xi' + i y\eta }
  \]
  So the symbol of $Q = P \phi H$ is
  \[
    Q(x,y,\xi,\eta) = \int d\xi' P(x,y,\xi') {\cal F}_x\phi(\xi'-\xi,y) e^{i x(\xi'-\xi)}H(\xi,\eta)
  \]
  \[
    = \left(\int d\xi' P(x,y,\xi+\xi') {\cal F}_x\phi(\xi',y) e^{i x\xi'}\right) H(\xi,\eta)
  \]
  From the definition of $S^0_{1,0}$, for $(x,y)$ ranging over a compact $K \subset \bR^n$ , and any $\alpha \in {\bf Z}_+^m$, there is $C_{K,|\alpha|} > 0$ so that
  \[
    |\partial^{\alpha}_{\xi} P(x,y,\xi)| \le C_{K,|\alpha|}(1 + |\xi|)^{-|\alpha|}
  \]
  so for $(x,y) \in K, \alpha=(\alpha_1,\alpha_2) \in {\bf Z}_+^m \times {\bf Z}_+^{n-m}$,
  \[
    |\partial_{\xi,\eta}^{\alpha} Q(x,y,\xi,\eta)|
  \]
  \[
    \le \sum_{\alpha_1' \le \alpha_1} \left|\left(\partial_{\xi}^{\alpha_1'}  \int d\xi' P(x,y,\xi+\xi') {\cal F}_x\phi(\xi',y) e^{i x\xi'}\right)\partial_{\xi}^{\alpha_1-\alpha_1'} \partial_{\eta}^{\alpha_2}H(\xi,\eta)       \right|
  \]
  \[
    \le C \sum_{\alpha_1' \le \alpha_1} \left|\left(  \int d\xi' (1 + |\xi+\xi'|)^{-|\alpha_1'|} {\cal F}_x\phi(\xi',y) e^{i x\xi'}\right)\partial_{\xi}^{\alpha_1-\alpha_1'} \partial_{\eta}^{\alpha_2}H(\xi,\eta)       \right|
  \]
  Rearranging the conclusion of Lemma \ref{thm:prebao},
  \[
    (1 + |\xi + \xi'|)^{-k} \le (1+|\xi|)^k(1+|\xi'|)^{-k},
  \]
  so
  \[
    |\partial_{\xi,\eta}^{\alpha} Q(x,y,\xi,\eta)| \le C \sum_{\alpha_1' \le \alpha_1} (1 + |\xi|)^{-|\alpha_1'|}|\partial_{\xi}^{\alpha_1-\alpha_1'}\partial_{\eta}^{\alpha_2}H(\xi,\eta) |
  \]
  \[
    \le C \sum_{\alpha_1' \le \alpha_1} (1 + |\xi|)^{-|\alpha_1'|}(1 + |(\xi,\eta)|)^{-|\alpha_1|+|\alpha_1'|-\alpha_2}
  \]
  since $H \in S^0_{1,0}(\bR^n)$. From norm equivalence, can replace $|(\xi,\eta)|$ with $|\xi| + |\eta|$   for the price of changing $C$.  So the above is
  \[
    \le C \sum_{\alpha_1' \le \alpha_1} (1 + |\xi|)^{-|\alpha_1'|}(1 + |\xi| + |\eta|)^{-|\alpha_1|+|\alpha_1'|-|\alpha_2|}
  \]
  \[
    \le C \sum_{\alpha_1' \le \alpha_1} (1 + |\xi|+ |\eta|)^{-|\alpha_1'|}(1 + |\xi| + |\eta|)^{-|\alpha_1|+|\alpha_1'|-|\alpha_2|}
  \]
  \[
    \le C (1 + |\xi| + |\eta|)^{-|\alpha_1|-|\alpha_2|} \le C(1 + |(\xi,\eta)|)^{-|\alpha|}
  \]
  whence $Q \in S^{0}_{1,0}(\bR^n)$.

>>>>

\section{Local Analysis of Surface Source Field}
$k \times  k$ symmetric hyperbolic system: in $\bR^{n+1}$. Suppose that $u \in L^2_{\rm loc}(\bR^{n+1},\bR^k)$ is a weak solution of
\begin{equation}
  \label{eqn:shs}
  (\sum_{i=0}^n A_i\partial_i ) u \in L^2_{\rm loc}(\bR^{n+1},\bR^k)
\end{equation}
The coefficieent matrices $A_i \in C^{\infty}(\bR^n, \bR^{k \times
  k}), i=0,...,n$ are symmetric, $A_0$ is positive definite.

Notation:$x_0=t$, $\partial_t=\partial_0$, $\bx = (x_1,...,x_{n-1})$,
$\partial_x=(\partial_1,...\partial_{n-1})$, $x_n=z$, $\partial_z =
\partial_{n}$, $M=A_0(\bx)$, $A = (A_1,...,A_{n-1}$, $L=A_{n}$.

Asymptotic solution 
\[
u(t,\bx,z) \approx e^{i\omega(t + \psi(\bx,z))} U(\bx,z)\sum_{n=0}^{\infty}
a_n(t,\bx,z)
\]
Substitute first term in equation \ref{eqn:shs}, obtain
\[
(M\partial_t + A\cdot \partial_x + L \partial_z)u(t,\bx,z) =
\]
\[
 e^{i\omega(t + \psi(\bx,z))}\left[ i\omega (M + A
\cdot \partial_x \psi(\bx,z) + L \partial_z
\psi(t,\bx,z))U(\bx,z)a_0(t,\bx,z) \right.
\]
\[
\left. + M(\bx,z) U(\bx,z) \partial_t a_0(t,\bx,z) + \partial_x
(a_0(t,\bx,z) U(\bx,z))\cdot A + L\partial_z (a_0(t,\bx,z)U(\bx,z))\right]= 0
\]
Assume $\Gamma$ is an open neighborhood of $0$ in $\bR^{n-1}$, $Z>0$ so that for each
$\xi \in \Gamma, |\xi|=1$ and $|z| < Z$, there are $l$ independent
solutions
$(\zeta_1(\bx,z,\xi),U_1(\bx,z,\xi)),...,(\zeta_l(\bx,z,\xi), U_l(\bx,z,\xi))$ of
\[
 (M(\bx,z) + A\cdot \xi + L \zeta) U=0.
\]
The $U$s are orthogonal, and might as well normalize by
$|U|=1$. For each $\xi \in \Gamma$, construct by method of characteristics solutions
$\psi_1,...,\psi_l$ of 
\[
\partial_z \psi_i(\bx,z,\xi) = \zeta_i(\bx,z,\partial_x\psi(\bx,z,\xi))
\]
with $\psi_l(\bx,0,\xi) =\xi \cdot x$. The corresponding Hamiltonian
system for $(\bx_i(z;\bx_0,\xi_0),\xi_i(z;\bx_0,\xi_0))$ with
$(\bx_0,\xi_0) \in \Gamma$ is
\begin{equation}
  \label{eqn:zetahe1}
  \frac{d\bx_i}{dz} = - \partial_{\xi}\zeta_i(\bx_i,z,\xi_i),\,
  \bx_i(0;\bx_0,\xi_0) = \bx_0;
\end{equation}
\begin{equation}
  \label{eqn:zetahe2}
  \frac{d\xi_i}{dz}
  = \partial_x\zeta_i(\bx_i,z,\xi_i),\, \xi_i(0;\bx_0,\xi_0) = \xi_0.
\end{equation}
and
\[
  \psi_l(\bx_i(z;\bx_0,\xi_0),z,\xi_i(z;\bx_0,\xi_0))= \bx_0\cdot\xi_0
\]
\begin{equation}
  \label{eqn:psihe}
- \int_0^z ds \xi(s;\bx_0,\xi_0)\cdot \partial_{\xi}\zeta_i(\bx_i(s;\bx_0,\xi_0),s,\xi_i(s;\bx_0,\xi_0))
\end{equation}

$\Pi_0$ = projection on null space $V_0$ of $M(t,\bx)$, $\Pi_1=I-\Pi_0$ = projection on range $V_1$. Denote the rank of $M$ by $l={\rm dim} V_1$ Then

\section{Symmetric Hyperbolic Systems}

@@

Notation:$x_0=t$, $\partial_t=\partial_0$, $\bx = (x_1,...,x_n)$, $D=(\partial_1,...\partial_n)$
\[
  K(t,\bx,D)= \sum_{i=1}^n A_i(t,\bx)\partial_i, \, M(t,\bx) = A_0(t,\bx).
\]
If $M$ is positive definite, trace properties coverd by standard theory (above). Let $\Pi_0(t,\bx)$ = projection on null space $V_0$ of $M(t,\bx)$, $\Pi_1=I-\Pi_0$ = projection on range $V_1$. Denote the rank of $M$ by $l={\rm dim} V_1$ Then
\[
  M\partial_t u + Ku = \Pi_1 M \partial_t \Pi_1 u + \sum_{\alpha,\beta=0,1} \Pi_{\alpha}K\Pi_{\beta}u + \mbox{ l.o.t. }
\]
Since the ranges are orthogonal,
\begin{eqnarray}
  \Pi_1 M \partial_t \Pi_1 u + \Pi_1 K \Pi_1 u + \Pi_1 K \Pi_0 u & \in & L^2_{\rm loc}(\bR^{n+1},V_1),
  \label{eqn:decomp1} \\
  \Pi_0 K \Pi_0 u + \Pi_0 K \Pi_1 u & \in & L^2_{\rm loc}(\bR^{n+1},V_0)
  \label{eqn:decomp0}
\end{eqnarray}
Set $K_{\alpha,\beta} = \Pi_{\alpha}K\Pi_{\beta}$.

@@

% Suppose that $\Gamma_0, \Gamma \subset T^*(\bR^n)$ are conic open sets with $\overbar{\Gamma_0 \subset \Gamma$ and $\delta t >0$. Assume that  that for $|t|\le \delta t$ and $(\bx,\xi) \in Gamma$, $K_{00}(0,\bx,\xi)$ is invertible as a map $V_0 \rightarrow V_0$.
Let  $L_{00}(t,\bx,\xi) \in C^{\infty}(\bR, S^{-1}(\bR^n))$ be inverse to $K_{0,0}(t,\bx,\xi)$ on $V_0$: that is,
\[
  K_{0,0}(t,\bx,\xi)L_{0,0}(t,\bx,\xi) v=v=L_{0,0}(t,\bx,\xi)K_{0,0}(t,\bx,\xi)v
\]
for all $v \in V_0$. Construct $L_{0,0}$ to be homogeneous of degree -1 outside of a neighborhood of $\xi=0$, with $V_1$ an invariant subspace for $L_{0,0}(t,\bx,\xi)$ on which it vanishes. It follows that $L_{0,0}$ is symmetric, and that
\[
  \Pi_0 u - L_{0,0}K_{0,0}\Pi_u = \Pi_0 u - L_{0,0}K_{0,0}u = \Pi_0 u + L_{0,0}K_{0,1}u \in H^{1}_{\rm loc}(\bR^{n+1})^k
\]
so
\[
  K_{1,0}u + K_{1,0}L_{0,0}K_{0,1}u \in L^2 _{\rm loc}(\bR^{n+1})^k
\]
Define
\[
  \tilde{K} = K_{11} - K_{10}L_{00}K_{01}.
\]
Then equation \ref{eqn:decomp1} can be rewritten
\begin{equation}
  \label{eqn:shs1}
  M\partial_t u_1 + \tilde{K}u_1 \in L^2_{\rm loc}(\bR^{n+1},V_1)
\end{equation}
Note that for each $t \in \bR, (\bx,\xi) \in T^*(\bR^n)$, both $V_0$ and $V_1$ are invariant subspaces of $\tilde{K}(t,\bx,\xi)$, and $V_0 \subset {\rm ker}\tilde{K}(t,\bx,\xi)$. Also, $M$ is invertible when restricted to $V_1 = {\rm Rng} M = {\rm Rng } \Pi_1$ , but not (necessarily) positive definite.

Restricted determinant: if $V$ is an invariant subspace of $A$, then ${\rm det}_{V} A$ is the determinant of the matrix of $A$ in any orthonormal basis of $V$.
For $(t,\bx,\tau,\xi) \in T^*(\bR^n)$, define the restricted characteristic polynomial
\[
  {\cal C}(t,\bx,\tau,\xi) = {\rm det}_{V_1} (M(t,\bx)\tau + \tilde{K}(t,\bx,\xi) )= 0
\]
Since $V_0$ and $V_1$ are invariant subspaces of the matrix in parentheses, and $V_0$ is (contained in) its null space, there are at most $l={\rm dim}V_1$ non-zero roots in $\tau$ for $\xi \ne 0$.

@@

For each $\tau_i, i =1,...m$, choose $U_i(t,\bx,\xi) \in C^{\infty}(\bR \times T^*(\bR^n),V_1(t,\bx))$,  so that
\[
  \tau_i M(\bx) U_i(t,\bx,\xi) + \tilde{K}(t,\bx,\xi) U_i(t,\bx,\xi)=0, \, i=1,..,m.
\]
$U_1,...,U_m$ span a subspace $\tilde{V}_1(t,\bx,\xi)$. Scale $U_i$ so that $|U_i(t,\bx,\xi)| = 1$.

Note that $\tau_i(t,\bx,\xi), i=1,...,m$ are homogeneous of order 1 in $\xi$ and smooth in $\bx$, $U_i(t,\bx,\xi), i=1,...,m$ are homogeneous of order 0 in $\xi$, smooth in $\bx$. So both are symbol-valued functions, of orders 1 and 0 respectively. Since the $U$'s must be orthogonal, $U_i^TU_j = \delta_{ij}$.

@@

Set $u=(p,v_x,v_z), \bx=x, x_2=z. \xi=\xi_x$. Then \ref{eqn:awe} takes the form \ref{eqn:shs} with
\[
  L =
  \left(
    \begin{array}{ccc}
      0 & 0 & 1\\
      0 & 0 & 0\\
      1 & 0 & 0
    \end{array}
  \right),
  M ={\rm diag}\left(\frac{1}{\kappa},\rho,\rho\right),
  A =
 \left(
    \begin{array}{ccc}
      0 & 1 & 0\\
      1 & 0 & 0\\
      0 & 0 & 0
    \end{array}
  \right),
\]
\[
  M + A\xi + L\zeta =
  \left(
    \begin{array}{ccc}
      \frac{1}{\kappa} & \xi & \zeta \\
      \xi & \rho & 0 \\
      \zeta & 0 & \rho
    \end{array}
  \right)
\]
Determinant is
\[
  {\rm det} = \rho\left(\frac{\rho}{\kappa} - \xi^2 - \zeta^2\right)
\]
Therefore take $\Gamma = \{\xi: |\xi| \lt \mbox{inf
}\{\sqrt{\rho(\bx,z)/kappa(\bx,z)}, \mbox{ all } |z| < Z\}$. For $\xi
\in \Gamma$, there are two roots $\zeta = \pm \sqrt{\rho/\kappa - \xi^2}.

So $V_0={\rm span}(\{e2\}),\, V_1={\rm span}(\{e1,e3\}), \Pi_0 = {\rm diag}(0,1,0)$ 
\[
  K(t,\bx,\xi) =  A_1(\bx) \xi_1 + A_2(\bx) \xi_2 =
  \left(
    \begin{array}{ccc}
      \frac{1}{\kappa(\bx)}\omega & \xi_x & 0 \\
      \xi_x & \rho(\bx) \omega & 0 \\
      0 & 0 & \rho(\bx) \omega
    \end{array}
  \right)
\]
whence $K_{0,0} = {\rm diag}(0, \rho(\bx) \omega, 0)$.
\[
  K_{1,1}(t,\bx,\xi) =
  \left(
    \begin{array}{ccc}
      \frac{1}{\kappa(\bx)}\omega & 0 & 0 \\
      0 & 0 & 0 \\
      0 & 0 & \rho(\bx) \omega
    \end{array}
  \right),
\]
\[
  K_{0,1}(t,\bx,\xi) =
  \left(
    \begin{array}{ccc}
      0 & \xi_x & 0 \\
      0 & 0 & 0 \\
      0 & 0 & 0
    \end{array}
  \right)
\]
and $K_{1,0} = K_{0,1}^T$.

@@

\begin{proof}
  For $u \in \Ciz(\bR^n)$,
  \[
    {\cal F}_x(Hu)(\xi',y) = \int  d\eta H(\xi',\eta')\hat{u}(\xi',\eta)e^{ i y \eta}
  \]
  So
  \[
    (P\phi H)u(x,y) = \int d \xi P(x,y,\xi) {\cal F}_x(\phi Hu)(\xi,y)e^{i x\xi}
  \]
  \[
    =\int d \xi' \int d \xi P(x,y,\xi) {\cal F}_x\phi(\xi-\xi',y) {\cal F}_x(Hu)(\xi',y)e^{i x\xi}
  \]
  \[
   =\int d \xi' \int d \xi \int d\eta P(x,y,\xi) {\cal F}_x\phi(\xi-\xi',y) H(\xi',\eta)\hat{u}(\xi',\eta)e^{i x\xi + i y\eta }
  \]
  \[
    =\int d \xi' \int d \xi \int d\eta P(x,y,\xi) {\cal F}_x\phi(\xi-\xi',y) e^{ix(\xi-\xi')}H(\xi',\eta)\hat{u}(\xi',\eta)e^{i x\xi' + i y\eta }
  \]
  So the symbol of $Q = P \phi H$ is
  \[
    Q(x,y,\xi,\eta) = \int d\xi' P(x,y,\xi') {\cal F}_x\phi(\xi'-\xi,y) e^{i x(\xi'-\xi)}H(\xi,\eta)
  \]
  \[
    = \left(\int d\xi' P(x,y,\xi+\xi') {\cal F}_x\phi(\xi',y) e^{i x\xi'}\right) H(\xi,\eta)
  \]
  From the definition of $S^0_{1,0}$, for $(x,y)$ ranging over a compact $K \subset \bR^n$ , and any $\alpha \in {\bf Z}_+^m$, there is $C_{K,|\alpha|} > 0$ so that
  \[
    |\partial^{\alpha}_{\xi} P(x,y,\xi)| \le C_{K,|\alpha|}(1 + |\xi|)^{-|\alpha|}
  \]
  so for $(x,y) \in K, \alpha=(\alpha_1,\alpha_2) \in {\bf Z}_+^m \times {\bf Z}_+^{n-m}$,
  \[
    |\partial_{\xi,\eta}^{\alpha} Q(x,y,\xi,\eta)|
  \]
  \[
    \le \sum_{\alpha_1' \le \alpha_1} \left|\left(\partial_{\xi}^{\alpha_1'}  \int d\xi' P(x,y,\xi+\xi') {\cal F}_x\phi(\xi',y) e^{i x\xi'}\right)\partial_{\xi}^{\alpha_1-\alpha_1'} \partial_{\eta}^{\alpha_2}H(\xi,\eta)       \right|
  \]
  \[
    \le C \sum_{\alpha_1' \le \alpha_1} \left|\left(  \int d\xi' (1 + |\xi+\xi'|)^{-|\alpha_1'|} {\cal F}_x\phi(\xi',y) e^{i x\xi'}\right)\partial_{\xi}^{\alpha_1-\alpha_1'} \partial_{\eta}^{\alpha_2}H(\xi,\eta)       \right|
  \]
  Rearranging the conclusion of Lemma \ref{thm:prebao},
  \[
    (1 + |\xi + \xi'|)^{-k} \le (1+|\xi'|)^k(1+|\xi|)^{-k},
  \]
  so
  \begin{equation}
    \label{eqn:qbound}
    |\partial_{\xi,\eta}^{\alpha} Q(x,y,\xi,\eta)| \le C \sum_{\alpha_1' \le \alpha_1} (1 + |\xi|)^{-|\alpha_1'|}|\partial_{\xi}^{\alpha_1-\alpha_1'}\partial_{\eta}^{\alpha_2}H(\xi,\eta) |
  \end{equation}
  Recall that $ES(H) \cap {\cal N} = \emptyset$. That is, there is $s>0$ so that for
  $k,N \in {\bf Z}_+, \beta \in {\bf Z_+}^n$ with $|\beta| \le k$, there are $C_{k,N} \ge 0$ so that for $|\xi| \le s|\eta|$,
  \[
    |\partial_{\xi,\eta}^{\beta}H(\xi,\eta)| \le C_{k,N} |(\xi,\eta)|^{-N}
  \]
  In particular, if $k, N = |\alpha|$, then the integrand in each summand on the RHS of inequality \ref{eqn:qbound} is bounded by an $|\alpha|$-dependent multiple of $(1+|(\xi,\eta)|)^{-|\alpha|}$ in the conic neighborhood of ${\cal N}$ defined by $|\xi| \le s|\eta|$.

  On the other hand, note that
  \[
    s|\eta| \le |\xi| \Rightarrow 1 + |(\xi,\eta)| \le 1 + |\xi| + |\eta| 
    \le \frac{1+s}{s} (1+ |\xi|) 
  \]
  hence
  \[
    (1 + |\xi|)^{-|\alpha_1'|} \le \left(\frac{s}{1+s}(1+|(\xi,\eta)|)\right)^{-|\alpha_1'|}   
  \]
  In the complement defined by $|\xi|\ge s|\eta|$, the $\alpha_1'$  summand on the RHS of inequality \ref{eqn:qbound} is bounded by a multiple of
  \[
    \left(\frac{s}{1+s}(1 + |(\xi,\eta)|)\right)^{-|\alpha_1'|}|\partial_{\xi}^{\alpha_1-\alpha_1'}\partial_{\eta}^{\alpha_2}H(\xi,\eta) |
  \]
  which is in turn bounded by a multiple of
  \[
    \left(\frac{s}{1+s}\right)^{-|\alpha|} (1+|(\xi,\eta)|)^{-|\alpha|}
  \]
  because $H \in S^0(\bR^n)$.

  These bounds together cover all of $T^*(\bR^n)$, so imply the bounds necessary to conclude that $Q \in S^0(\bR^n)$.

  The assertion about the essential support is equivalent to existence of $C>0$ for any $\beta \in {\bf Z}_+^n, N \in {\bf Z}_+$ so that
  \[
    |(\partial_{\xi,\eta}^{\beta} Q)(x,y,\xi, \eta)| \le C(1+|(\xi,\eta)|)^{-N}
  \]
  for $\xi \notin ES(P)$ or $(\xi,\eta) \notin ES(H)$.
\end{proof}

\section{Computing Q}

\subsection{Cauchy problem}
\[
  \partial_t S(t) = -K S(t), S(0)=I
\]
\[
  \partial_t S(-t) = -S(-t) \partial_t S(t) S(-t) = S(-t)K
\]
\[
  \partial_t \delta S(t) = - \delta K S(t) - K \delta S(t)
\]
\[
  \partial_t S(-t)\delta S(t) = S(-t)K\delta S(t) - S(-t) \delta K S(t) - S(-t)K \delta S(t)
\]
\begin{equation}
  \label{eqn:qevol1}
  =  -S(-t)\delta K S(t)
\end{equation}

\subsection{PsiDO RHS}
Suppose that $K \in OPS^1$ is skew-adjoint, at least in principal part: $K_1^*=-K_1$. Then there is unitary $U \in OPS^0$ so that $U(x,\xi)^*K_1(x,\xi)U(x,\xi) = i\Lambda(x,\xi) = i\mbox{diag}(\lambda_1(x,\xi),...\lambda_k(x,\xi))$, with scalar $\lambda_j \in OPS^1, j=1,...,k$ (in fact, homogeneous of degree 1). Hence
\[
  \partial_t S(t) = -iU \Lambda U^*S(t) + RS(t), R \in OPS^0 
\]
Write $\tilde{S} = U^*SU$. Then 
\[
  \partial_t \tilde{S}(t) = -i\Lambda \tilde{S}(t) + \mbox{ mod } OPS^0 
\]
If $u^0 = (u^0_1,...,u^0_k)$, then $\tilde{u}(t) = \tilde{S}(t)u^0$ satisfies
\[
  \partial_t \tilde{u}(t) = -i\Lambda \tilde{u}(t) + ...
\]
so $\tilde{u}_i$ solves
\[
  \partial_t \tilde{u}_i(t) = -i\lambda_i \tilde{u}_i(t), \, i=1,...,k
\]
Let $\tilde{S}_i$ solve
\[
  \partial_t \tilde{S}_i(t) = - i\lambda_i \tilde{S}_i(t)
\]
Then
\[
  \tilde{u}_i(t) = \tilde{S}_i(t) u^0_i = (\tilde{S}(t)u^0)_i 
\]
whence
\[
  \tilde{S} = \mbox{diag}(\tilde{S}_1,....,\tilde{S}_k).
\]

From equation \ref{eqn:qevol1},
\[
  \tilde{Q}_i(t) = \tilde{S}_i(-t)\delta \tilde{S}_i(t)
\]
satisfies
\[
  \partial \tilde{Q}_i(t) = -i\tilde{S}_i(-t)\delta \lambda_i \tilde{S}_i(t), \, i=1,,,.k.
\]
and $\tilde{Q} = \mbox{diag}(\tilde{Q}_1,...,\tilde{Q}_k)$.
From \cite{Tay:81}, Egorov's Theorem (Section VIII.1),
\[
  \tilde{Q}_i(t; x,\xi) = -i \int_0^t ds \,\delta \lambda_i(y_i(s;x,\xi),\eta_i(s;x,\xi))
\]
in which $(y_i(s;x,\xi),\eta_i(s;x,\xi))$ is the integral curve of the Hamiltonian vector field
\[
  H_i(x,\xi) = (\partial_{\xi}\lambda_i(x,\xi), - \partial_x\lambda_i(x,\xi))
\]
with $y_i(0;x,\xi)=x, \eta_i(0;x,\xi)=\xi$.
